\protect Connecting every bit of knowledge: \\ The structure of Wikipedia's First Link Network

### 2016-09-15 writeup/2016-04wikipedia-network/correspondence/2016-08-22-compsci-reviewers/2016-09-12-response.body.tex

>>>>

\textbf{Regarding the novelty of our work, while there have been a handful of explorations described on the internet (e.g. in blog posts), to our knowledge we are providing the first academic description of the first-link network.}

\textbf{
In our analysis of the network's structure, we also develop traveral funnels, a method for characterizing influence in a directed network.
}
